dispRity demo

### 2015-09-30 doc/dispRity.demo.Rnw
demo vignette updated

<<Quick go, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
## Splitting the data
sliced_data <- time.series(BeckLee_mat99, BeckLee_tree, method = "continuous",
    model = "acctran", time = 5, FADLAD = BeckLee_ages)

@@

<<boot.matrix3>>=
#Let's do a full rarefaction on the crown/stem data for later
crown_stemBS <- boot.matrix(crown_stem, rarefaction = TRUE)
## And just bootstrapping for the time binning/slicing
time_binsBS <- boot.matrix(time_bins)
time_slicesBS <- boot.matrix(time_slices)

@@

## Or even better, from the bootstrapped data
disp_crown_stemBS <- dispRity(crown_stemBS, metric = c(sum, ranges))
## Note that the bootstrapped + rarefied data takes some time to run (it's
## calculating disparity from 46 matrices!)
disp_time_binsBS <- dispRity(time_binsBS, metric = c(sum, ranges))
disp_time_slicesBS <- dispRity(time_slicesBS, metric = c(sum, ranges))
@

@@

<<plot1, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
plot(disp_crown_stemBS, type = "discrete")
@

@@

<<plot2, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
plot(disp_crown_stemBS, type = "discrete", diversity = TRUE)
@

@@

<<plot3, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
plot(disp_crown_stemBS, type = "discrete", diversity = TRUE, rarefaction = 20)
@

@@

<<plot4, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
plot(disp_crown_stemBS, type = "discrete", diversity = TRUE, rarefaction = "plot")
@

@@

<<plot5, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
plot(disp_time_binsBS, type = "discrete", discrete_type = "line")
@

@@

<<plot6, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
plot(disp_time_slicesBS, type = "continuous")
@

@@

<<plot7, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
op<-par(bty="n")
plot(disp_time_slicesBS, CI = c(50, 75, 95), cent.tend = median, type = "continuous",
    diversity = TRUE, col = c("black", "red", "orange", "yellow"), ylab = c("Disparity", "Diversity"),
    xlab = "Time (in in units from past to present)", time.series = FALSE, main = "Many options...")
par(op)
@

\section{What's left?}
\label{whatsleft}

>>>>

<<Quick go, fig.width=5, fig.height=5, out.width='.5\\linewidth'>>=
## Splitting the data
sliced_data <- time.series(BeckLee_mat99, BeckLee_tree, method = "continuous",
    model = "acctran", time = 5, FADLAD = BeckLee_ages)

@@

<<boot.matrix3>>=
## Let's do a full rarefaction on the crown/stem data for later
crown_stemBS <- boot.matrix(crown_stem, rarefaction = TRUE)
## And just bootstrapping for the time binning/slicing
time_binsBS <- boot.matrix(time_bins)
time_slicesBS <- boot.matrix(time_slices)

@@

## Or even better, from the bootstrapped data
disp_crown_stemBS <- dispRity(crown_stemBS, metric = c(sum, ranges))
## Note that the bootstrapped + rarefied data takes some time to run (it's
## calculating disparity from 46 matrices!)

## Let's calculate a different metric for the disparity-through-time analysis
disp_time_binsBS <- dispRity(time_binsBS, metric = c(median, centroids))
disp_time_slicesBS <- dispRity(time_slicesBS, metric = c(median, centroids))
@

@@

<<plot1, fig.width=15, fig.height=5, out.width='1\\linewidth'>>=
## Graphical options
quartz(width = 15, height = 5) ; par(mfrow = (c(1,3)), bty = "n")

## Plotting the score for both groups
plot(disp_crown_stemBS, type = "discrete" , ylim = c(25,40))

## Same one with the number of taxa for each data set
plot(disp_crown_stemBS, type = "discrete", diversity = TRUE, ylim = c(25,40))

## Same one with rarefied data (note how that affects the diversity data as well!)
plot(disp_crown_stemBS, type = "discrete", diversity = TRUE, rarefaction = 20, ylim = c(25,40))
@

@@

@@

@@

<<plot2, fig.width=5, fig.height=8, out.width='0.5\\linewidth'>>=
## Graphical options
par(bty = "n")

## The rarefaction curves
plot(disp_crown_stemBS, type = "discrete", diversity = TRUE, rarefaction = "plot")
## Note that the function automatically draws the curves for each series and splits
## the plot screen accordingly.
@

@@

<<plot3, fig.width=10, fig.height=5, out.width='1\\linewidth'>>=
## Graphical options
quartz(width = 10, height = 5) ; par(mfrow = (c(1,2)), bty = "n")

## The disparity-through-time data in a time-binned way
plot(disp_time_binsBS, type = "discrete", discrete_type = "line")

## The disparity-through-time data in a time-sliced ways
plot(disp_time_slicesBS, type = "continuous")

@

@@

<<plot4, fig.width=5, fig.height=5, out.width='.5\\linewidth'>>=
## Graphical options
par(bty = "n")

## First, plotting the continuous data
plot(disp_time_slicesBS, type = "continuous", ylim=c(0.5,2))

## Second, adding the discrete data
par(new = TRUE)
plot(disp_time_binsBS, type = "discrete", discrete_type = "line", ylim=c(0.5,2), xlab="", ylab="")
@

@@

<<plot5, fig.width=5, fig.height=5, out.width='.5\\linewidth'>>=
## Graphical options
par(bty = "n")

## A plot with many options!
plot(disp_time_slicesBS, CI = c(50, 75, 95), cent.tend = median, type = "continuous",
    diversity = TRUE, col = c("black", "red", "orange", "yellow"), ylab = c("Disparity", "Diversity"),
    xlab = "Time (in in units from past to present)", time.series = FALSE, main = "Many options...")
@

\section{What's left?}
\label{whatsleft}
\subsection{Some statistics}
\subsection{Users defined metrics}
\subsection{More user defined stuff}

### 2015-09-30 doc/dispRity.demo.tex
demo vignette updated

\hlcom{## Summarising the results}
\hlkwd{summary}\hlstd{(sum_of_ranges)}
\end{alltt}
\begin{verbatim}
##      series  n  mean  2.5%   25%   75% 97.5%
## 1 133.51104  3 17.57  0.00 15.51 24.35 24.35
## 2 100.13328 14 51.76 45.88 50.30 53.78 56.73
## 3  66.75552 23 64.41 59.89 62.89 66.17 68.61
## 4  33.37776 11 42.57 36.65 40.95 44.39 46.82
## 5         0 10 40.53 34.39 38.60 42.76 45.36
\end{verbatim}
\begin{alltt}
\hlkwd{plot}\hlstd{(sum_of_ranges,} \hlkwc{type} \hlstd{=} \hlstr{"continuous"}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-Quick_go-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{#Let's do a full rarefaction on the crown/stem data for later}
\hlstd{crown_stemBS} \hlkwb{<-} \hlkwd{boot.matrix}\hlstd{(crown_stem,} \hlkwc{rarefaction} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\hlcom{## And just bootstrapping for the time binning/slicing}
\hlstd{time_binsBS} \hlkwb{<-} \hlkwd{boot.matrix}\hlstd{(time_bins)}
\hlstd{time_slicesBS} \hlkwb{<-} \hlkwd{boot.matrix}\hlstd{(time_slices)}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## For example, let's calculate the sum of ranges from our crown/stem mammals}
\hlkwd{dispRity}\hlstd{(crown_stem,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(sum, ranges))}
\end{alltt}
\begin{verbatim}
## Disparity measurements across 2 series for 50 taxa. 
## Series:
## crown, stem.
## Disparity calculated as: sum ranges for 48 dimensions.
## Data was split using custom method.
\end{verbatim}
\begin{alltt}
\hlcom{## Or even better, from the bootstrapped data}
\hlstd{disp_crown_stemBS} \hlkwb{<-} \hlkwd{dispRity}\hlstd{(crown_stemBS,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(sum, ranges))}
\hlcom{## Note that the bootstrapped + rarefied data takes some time to run (it's}
\hlcom{## calculating disparity from 46 matrices!)}
\hlstd{disp_time_binsBS} \hlkwb{<-} \hlkwd{dispRity}\hlstd{(time_binsBS,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(sum, ranges))}
\hlstd{disp_time_slicesBS} \hlkwb{<-} \hlkwd{dispRity}\hlstd{(time_slicesBS,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(sum, ranges))}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Let's have a look at the disparity-through-time using in the time-binned data}
\hlkwd{summary}\hlstd{(disp_time_binsBS)}
\end{alltt}
\begin{verbatim}
##   series  n  mean  2.5%   25%   75% 97.5%
## 1 120-80  8 20.20 16.58 19.28 21.64 23.39
## 2  80-40 27 33.97 31.65 33.29 34.73 35.78
## 3   40-0 16 29.00 26.24 28.19 29.92 31.30
\end{verbatim}
\begin{alltt}
\hlcom{## The CIs are calculated as 50 and 95 and the central tendency is the mean by default.}
\hlcom{## We can change that easily by specifying different values in the options}
\hlkwd{summary}\hlstd{(disp_time_binsBS,} \hlkwc{CI} \hlstd{=} \hlnum{25}\hlstd{,} \hlkwc{cent.tend} \hlstd{= median,} \hlkwc{rounding} \hlstd{=} \hlnum{0}\hlstd{)}
\end{alltt}
\begin{verbatim}
##   series  n median 37.5% 62.5%
## 1 120-80  8     20    20    21
## 2  80-40 27     34    34    34
## 3   40-0 16     29    29    29
\end{verbatim}
\begin{alltt}
\hlcom{## Also, if we happen to have forgotten what was in the disp_time_binsBS object (as in which}
\hlcom{## options where used to modify the original matrix) we can use the recall option}
\hlkwd{summary}\hlstd{(disp_time_binsBS,} \hlkwc{recall} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## Disparity calculated as: sum ranges for 48 dimensions.
## Data was split using discrete method.
## Data was bootstrapped 1000 times, using the full bootstrap method.
##   series  n  mean  2.5%   25%   75% 97.5%
## 1 120-80  8 20.20 16.58 19.28 21.64 23.39
## 2  80-40 27 33.97 31.65 33.29 34.73 35.78
## 3   40-0 16 29.00 26.24 28.19 29.92 31.30
\end{verbatim}
\begin{alltt}
\hlcom{## Note that the recall just prints text. The output of summary.dispRity is always a data.frame}
\hlstd{summary_table} \hlkwb{<-} \hlkwd{summary}\hlstd{(disp_time_binsBS,} \hlkwc{recall} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## Disparity calculated as: sum ranges for 48 dimensions.
## Data was split using discrete method.
## Data was bootstrapped 1000 times, using the full bootstrap method.
\end{verbatim}
\begin{alltt}
\hlkwd{class}\hlstd{(summary_table)}
\end{alltt}
\begin{verbatim}
## [1] "data.frame"
\end{verbatim}
\begin{alltt}
\hlcom{## Finally we can see the results of the rarefaction analysis for the crown/stem data}
\hlkwd{head}\hlstd{(}\hlkwd{summary}\hlstd{(disp_crown_stemBS))}
\end{alltt}
\begin{verbatim}
##   series n  mean  2.5%   25%   75% 97.5%
## 1  crown 3 15.17 10.04 15.16 16.04 16.64
## 2  crown 4 18.39 14.83 18.34 19.42 19.95
## 3  crown 5 20.83 18.04 19.68 21.83 22.42
## 4  crown 6 22.70 19.20 21.75 23.76 24.41
## 5  crown 7 24.15 21.01 23.47 25.29 26.11
## 6  crown 8 25.44 22.06 24.77 26.48 27.43
\end{verbatim}
\begin{alltt}
\hlcom{## This outputs a longer table with all the variations of the number of crown/stem taxa}
\hlcom{## from the maximum (30 and 20) to the minimum (3)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-plot1-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-plot2-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{rarefaction} \hlstd{=} \hlnum{20}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-plot3-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{rarefaction} \hlstd{=} \hlstr{"plot"}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-plot4-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(disp_time_binsBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{discrete_type} \hlstd{=} \hlstr{"line"}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-plot5-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(disp_time_slicesBS,} \hlkwc{type} \hlstd{=} \hlstr{"continuous"}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-plot6-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{op}\hlkwb{<-}\hlkwd{par}\hlstd{(}\hlkwc{bty}\hlstd{=}\hlstr{"n"}\hlstd{)}
\hlkwd{plot}\hlstd{(disp_time_slicesBS,} \hlkwc{CI} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{50}\hlstd{,} \hlnum{75}\hlstd{,} \hlnum{95}\hlstd{),} \hlkwc{cent.tend} \hlstd{= median,} \hlkwc{type} \hlstd{=} \hlstr{"continuous"}\hlstd{,}
    \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"black"}\hlstd{,} \hlstr{"red"}\hlstd{,} \hlstr{"orange"}\hlstd{,} \hlstr{"yellow"}\hlstd{),} \hlkwc{ylab} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"Disparity"}\hlstd{,} \hlstr{"Diversity"}\hlstd{),}
    \hlkwc{xlab} \hlstd{=} \hlstr{"Time (in in units from past to present)"}\hlstd{,} \hlkwc{time.series} \hlstd{=} \hlnum{FALSE}\hlstd{,} \hlkwc{main} \hlstd{=} \hlstr{"Many options..."}\hlstd{)}
\hlkwd{par}\hlstd{(op)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth]{figure/minimal-plot7-1}

@@

\section{What's left?}
\label{whatsleft}

>>>>

\hlcom{## Summarising the results}
\hlkwd{summary}\hlstd{(sum_of_ranges)}
\end{alltt}
\begin{verbatim}
##      series  n  mean  2.5%   25%   75% 97.5%
## 1 133.51104  3 17.81  0.00 15.51 24.35 24.35
## 2 100.13328 14 52.05 45.80 49.90 54.50 57.67
## 3  66.75552 23 64.80 59.23 63.20 66.57 69.25
## 4  33.37776 11 42.95 37.94 41.40 44.77 47.43
## 5         0 10 40.94 35.13 39.22 42.69 46.13
\end{verbatim}
\begin{alltt}
\hlkwd{plot}\hlstd{(sum_of_ranges,} \hlkwc{type} \hlstd{=} \hlstr{"continuous"}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.5\linewidth]{figure/minimal-Quick_go-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Let's do a full rarefaction on the crown/stem data for later}
\hlstd{crown_stemBS} \hlkwb{<-} \hlkwd{boot.matrix}\hlstd{(crown_stem,} \hlkwc{rarefaction} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\hlcom{## And just bootstrapping for the time binning/slicing}
\hlstd{time_binsBS} \hlkwb{<-} \hlkwd{boot.matrix}\hlstd{(time_bins)}
\hlstd{time_slicesBS} \hlkwb{<-} \hlkwd{boot.matrix}\hlstd{(time_slices)}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## For example, let's calculate the sum of ranges from our crown/stem mammals}
\hlkwd{dispRity}\hlstd{(crown_stem,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(sum, ranges))}
\end{alltt}
\begin{verbatim}
## Disparity measurements across 2 series for 50 taxa. 
## Series:
## crown, stem.
## Disparity calculated as: sum ranges for 48 dimensions.
## Data was split using custom method.
\end{verbatim}
\begin{alltt}
\hlcom{## Or even better, from the bootstrapped data}
\hlstd{disp_crown_stemBS} \hlkwb{<-} \hlkwd{dispRity}\hlstd{(crown_stemBS,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(sum, ranges))}
\hlcom{## Note that the bootstrapped + rarefied data takes some time to run (it's}
\hlcom{## calculating disparity from 46 matrices!)}

\hlcom{## Let's calculate a different metric for the disparity-through-time analysis}
\hlstd{disp_time_binsBS} \hlkwb{<-} \hlkwd{dispRity}\hlstd{(time_binsBS,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(median, centroids))}
\hlstd{disp_time_slicesBS} \hlkwb{<-} \hlkwd{dispRity}\hlstd{(time_slicesBS,} \hlkwc{metric} \hlstd{=} \hlkwd{c}\hlstd{(median, centroids))}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Let's have a look at the disparity-through-time using in the time-binned data}
\hlkwd{summary}\hlstd{(disp_time_binsBS)}
\end{alltt}
\begin{verbatim}
##   series  n  mean  2.5%   25%   75% 97.5%
## 1 120-80  8 1.114 0.915 1.080 1.167 1.235
## 2  80-40 27 1.322 1.274 1.308 1.338 1.358
## 3   40-0 16 1.324 1.248 1.306 1.345 1.372
\end{verbatim}
\begin{alltt}
\hlcom{## The CIs are calculated as 50 and 95 and the central tendency is the mean by default.}
\hlcom{## We can change that easily by specifying different values in the options}
\hlkwd{summary}\hlstd{(disp_time_binsBS,} \hlkwc{CI} \hlstd{=} \hlnum{25}\hlstd{,} \hlkwc{cent.tend} \hlstd{= median,} \hlkwc{rounding} \hlstd{=} \hlnum{0}\hlstd{)}
\end{alltt}
\begin{verbatim}
##   series  n median 37.5% 62.5%
## 1 120-80  8      1     1     1
## 2  80-40 27      1     1     1
## 3   40-0 16      1     1     1
\end{verbatim}
\begin{alltt}
\hlcom{## Also, if we happen to have forgotten what was in the disp_time_binsBS object (as in which}
\hlcom{## options where used to modify the original matrix) we can use the recall option}
\hlkwd{summary}\hlstd{(disp_time_binsBS,} \hlkwc{recall} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## Disparity calculated as: median centroids for 48 dimensions.
## Data was split using discrete method.
## Data was bootstrapped 1000 times, using the full bootstrap method.
##   series  n  mean  2.5%   25%   75% 97.5%
## 1 120-80  8 1.114 0.915 1.080 1.167 1.235
## 2  80-40 27 1.322 1.274 1.308 1.338 1.358
## 3   40-0 16 1.324 1.248 1.306 1.345 1.372
\end{verbatim}
\begin{alltt}
\hlcom{## Note that the recall just prints text. The output of summary.dispRity is always a data.frame}
\hlstd{summary_table} \hlkwb{<-} \hlkwd{summary}\hlstd{(disp_time_binsBS,} \hlkwc{recall} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\end{alltt}
\begin{verbatim}
## Disparity calculated as: median centroids for 48 dimensions.
## Data was split using discrete method.
## Data was bootstrapped 1000 times, using the full bootstrap method.
\end{verbatim}
\begin{alltt}
\hlkwd{class}\hlstd{(summary_table)}
\end{alltt}
\begin{verbatim}
## [1] "data.frame"
\end{verbatim}
\begin{alltt}
\hlcom{## Finally we can see the results of the rarefaction analysis for the crown/stem data}
\hlkwd{head}\hlstd{(}\hlkwd{summary}\hlstd{(disp_crown_stemBS))}
\end{alltt}
\begin{verbatim}
##   series n  mean  2.5%   25%   75% 97.5%
## 1  crown 3 15.19 10.19 15.17 16.08 16.66
## 2  crown 4 18.47 14.97 18.40 19.41 19.89
## 3  crown 5 20.83 17.99 19.66 21.81 22.46
## 4  crown 6 22.60 18.84 21.68 23.77 24.51
## 5  crown 7 24.23 21.16 23.49 25.32 26.15
## 6  crown 8 25.46 22.40 24.82 26.51 27.42
\end{verbatim}
\begin{alltt}
\hlcom{## This outputs a longer table with all the variations of the number of crown/stem taxa}
\hlcom{## from the maximum (30 and 20) to the minimum (3)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Graphical options}
\hlkwd{quartz}\hlstd{(}\hlkwc{width} \hlstd{=} \hlnum{15}\hlstd{,} \hlkwc{height} \hlstd{=} \hlnum{5}\hlstd{) ;} \hlkwd{par}\hlstd{(}\hlkwc{mfrow} \hlstd{= (}\hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,}\hlnum{3}\hlstd{)),} \hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}

\hlcom{## Plotting the score for both groups}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"} \hlstd{,} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{25}\hlstd{,}\hlnum{40}\hlstd{))}

\hlcom{## Same one with the number of taxa for each data set}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{25}\hlstd{,}\hlnum{40}\hlstd{))}

\hlcom{## Same one with rarefied data (note how that affects the diversity data as well!)}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{rarefaction} \hlstd{=} \hlnum{20}\hlstd{,} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{25}\hlstd{,}\hlnum{40}\hlstd{))}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=1\linewidth]{figure/minimal-plot1-1}

@@

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Graphical options}
\hlkwd{par}\hlstd{(}\hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}

\hlcom{## The rarefaction curves}
\hlkwd{plot}\hlstd{(disp_crown_stemBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{rarefaction} \hlstd{=} \hlstr{"plot"}\hlstd{)}
\hlcom{## Note that the function automatically draws the curves for each series and splits}
\hlcom{## the plot screen accordingly.}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=0.5\linewidth]{figure/minimal-plot2-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Graphical options}
\hlkwd{quartz}\hlstd{(}\hlkwc{width} \hlstd{=} \hlnum{10}\hlstd{,} \hlkwc{height} \hlstd{=} \hlnum{5}\hlstd{) ;} \hlkwd{par}\hlstd{(}\hlkwc{mfrow} \hlstd{= (}\hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,}\hlnum{2}\hlstd{)),} \hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}

\hlcom{## The disparity-through-time data in a time-binned way}
\hlkwd{plot}\hlstd{(disp_time_binsBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{discrete_type} \hlstd{=} \hlstr{"line"}\hlstd{)}

\hlcom{## The disparity-through-time data in a time-sliced ways}
\hlkwd{plot}\hlstd{(disp_time_slicesBS,} \hlkwc{type} \hlstd{=} \hlstr{"continuous"}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=1\linewidth]{figure/minimal-plot3-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Graphical options}
\hlkwd{par}\hlstd{(}\hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}

\hlcom{## First, plotting the continuous data}
\hlkwd{plot}\hlstd{(disp_time_slicesBS,} \hlkwc{type} \hlstd{=} \hlstr{"continuous"}\hlstd{,} \hlkwc{ylim}\hlstd{=}\hlkwd{c}\hlstd{(}\hlnum{0.5}\hlstd{,}\hlnum{2}\hlstd{))}

\hlcom{## Second, adding the discrete data}
\hlkwd{par}\hlstd{(}\hlkwc{new} \hlstd{=} \hlnum{TRUE}\hlstd{)}
\hlkwd{plot}\hlstd{(disp_time_binsBS,} \hlkwc{type} \hlstd{=} \hlstr{"discrete"}\hlstd{,} \hlkwc{discrete_type} \hlstd{=} \hlstr{"line"}\hlstd{,} \hlkwc{ylim}\hlstd{=}\hlkwd{c}\hlstd{(}\hlnum{0.5}\hlstd{,}\hlnum{2}\hlstd{),} \hlkwc{xlab}\hlstd{=}\hlstr{""}\hlstd{,} \hlkwc{ylab}\hlstd{=}\hlstr{""}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.5\linewidth]{figure/minimal-plot4-1}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{## Graphical options}
\hlkwd{par}\hlstd{(}\hlkwc{bty} \hlstd{=} \hlstr{"n"}\hlstd{)}

\hlcom{## A plot with many options!}
\hlkwd{plot}\hlstd{(disp_time_slicesBS,} \hlkwc{CI} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{50}\hlstd{,} \hlnum{75}\hlstd{,} \hlnum{95}\hlstd{),} \hlkwc{cent.tend} \hlstd{= median,} \hlkwc{type} \hlstd{=} \hlstr{"continuous"}\hlstd{,}
    \hlkwc{diversity} \hlstd{=} \hlnum{TRUE}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"black"}\hlstd{,} \hlstr{"red"}\hlstd{,} \hlstr{"orange"}\hlstd{,} \hlstr{"yellow"}\hlstd{),} \hlkwc{ylab} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"Disparity"}\hlstd{,} \hlstr{"Diversity"}\hlstd{),}
    \hlkwc{xlab} \hlstd{=} \hlstr{"Time (in in units from past to present)"}\hlstd{,} \hlkwc{time.series} \hlstd{=} \hlnum{FALSE}\hlstd{,} \hlkwc{main} \hlstd{=} \hlstr{"Many options..."}\hlstd{)}
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.5\linewidth]{figure/minimal-plot5-1}

@@

\section{What's left?}
\label{whatsleft}
\subsection{Some statistics}
\subsection{Users defined metrics}
\subsection{More user defined stuff}
